\begin{thebibliography}{9}
  \bibitem{marine_current}
  AbuBakr S Bahaj et Luke E Myers

  \textit{Fundamentals applicable to the utilisation of marine current turbines for energy production}

  \bibitem{energy_management_smart_grids}
  Fady Y. Melhem. Optimization methods and

  energy management in ”Smart Grids”. Electric power.

  Université Bourgogne Franche-Comté, 2018. English.

  \bibitem{energy_demand_side}
  Hafiz Majid Hussain, Nadeem Javaid, Sohail Iqbal, Khursheed Aurangzeb et Musaed Alhussein

  \textit{An Efficient Demand Side Management System with a New Optimized Home Energy Management Controller in Smart Grid}

  \bibitem{communication_protocol}
  Sangam, Sahana \& Kulkarni, Sahana \& Jambotkar, Chaitanya. (2019).

  Smart Grid Communication Protocols. International Journal of Trend in Scientific Research and Development.

  Volume-3. 10.31142/ijtsrd21344.

  \bibitem{ev_smart_routing}
  Etesami, S. Rasoul \& Saad, Walid \& Mandayam, Narayan \& Poor, H. Vincent. (2017).

  Smart Routing of Electric Vehicles for Load Balancing in Smart Grids. 2599-2604. 10.1109/CDC.2017.8264036.

  \bibitem{nrg_consumption_scheduling}
  Stéphane Caron et George Kesidis

  Incentive-based Energy Consumption Scheduling Algorithms for the Smart Grid

  École Normale Supérieure

  The Pennsylvania State University

  \bibitem{demand_side_management}
  Peter Palensky et Dietmar Dietrich

  Demand Side Management: Demand Response, Intelligent Energy Systems, and Smart Loads

  \bibitem{stochastic_scheduling}
  Wencong Su, Jianhui Wang et Jaehyung Roh

  Stochastic Energy Scheduling in Microgrids With Intermittent Renewable Energy Resources


  \bibitem{Photovoltaic_Forecasting}
  Can Wan, Jian Zhao, Yonghua Song, CSEE, Zhao Xu, Jin Lin et Zechun Hu

  Photovoltaic and Solar Power Forecasting for Smart Grid Energy Management

  \bibitem{game_Theoretic_energy}
  Amir-Hamed Mohsenian-Rad, Vincent W. S. Wong, Juri Jatskevich, Robert Schober et Alberto Leon-Garcia

  Autonomous Demand-Side Management Based on Game-Theoretic Energy Consumption Scheduling for the Future Smart Grid

  \bibitem{Photovoltaic_life}
  V.M. Fthenakis et H.C. Kim

  Photovoltaics: Life-cycle analyses

  \bibitem{}
  Shane Duryea, Syed Islam et William Lawrance

  A Battery Management System for Stand Alone Photovoltaic Energy Systems

  School of Electrical and Computer Engineering

  \bibitem{}
  Rocco Papa

  Smart Energy in the Smart City Urban Planning for a Sustainable Future

  Romano Fistola Editors

  \bibitem{}
  ESMAP CEETI

  Planning Energy Efficient and Livable Cities

  \bibitem{}
  arcep

  L’empreinte carbone du numérique

  République française

  \bibitem{}
  Service de l’observation et des statistiques

  Chiffres clés du climat France et Monde

  République française

  \bibitem{}
  Paula Carroll et Cristina Requejo

  Smart Grid Topology Designs
\end{thebibliography}
